TODO: Funky active learning pun

### 2025-01-13 doc/paper.tex
refactor, update numbers in paper

\section{Experiments}\label{sec:experiments}
Several experiments are conducted with the two model-dataset combinations to research different scenarios for which active learning can be used.
\begin{itemize}
	\item Experiment 1: Starts with a minimal amount of data. In both cases these are 10 samples.
	\item Experiment 2: Starts with $15\%$ of the train dataset. 
	\item Experiment 3: Starts with $80\%$ of the train dataset.
\end{itemize}
In experiment 1, a random sample is chosen for each class in the datasets. \\
In each experiment, the random samples

@@

For each query method one model is trained. (I did not perform multiple runs)
Before starting the active learning process, each model is pre-trained using the samples in the initial labeled dataset for \textcolor{red}{X epochs}. In the case of pool-based query methods, 5 samples are queried for 250 iterations when training with samples from MNIST and 250 samples are queried for 50 iterations when training with instances from CIFAR. 
\\
\begin{itemize}
	\item Batch size for CNN is 128.
	\item Evaluation metrics. Metrics for evaluation (Accuracy, train error, confusion matrix, ...)
	\item How are the splits (initial pool, initial training data) generated
	\item initial labeled pool sizes
\end{itemize}

>>>>

\section{Experiments}\label{sec:experiments}
Several experiments are conducted with the two model-dataset combinations to research different scenarios for which active learning can be used.
\begin{itemize}
	\item Experiment 1: Starts with a minimal amount of data. In both cases these are 10 samples.
	\item Experiment 2: Starts with $10\%$ of the train dataset, resulting in $4800$ initial samples for MNIST and $4000$ \textcolor{red}{überprüfen} for CIFAR.
	\item Experiment 3: Starts with $50\%$ of the train dataset. Thus, $24.000$ labeled instances are chosen for MNIST and $20.000$ for CIFAR. \textcolor{red}{überprüfen ob das sinn ergibt}
\end{itemize}
In experiment 1, a random sample is chosen for each class in the datasets. \\
In each experiment, the random samples

@@

For each query method one model is trained. (I did not perform multiple runs)
Before starting the active learning process, each model is pre-trained using the samples in the initial labeled dataset for \textcolor{red}{X epochs}. In the case of pool-based query methods, 5 samples are queried for 250 iterations when training with samples from MNIST and 250 samples are queried for 50 iterations when training with instances from CIFAR. 
\\
\begin{itemize}
	\item Batch size for CNN is 128.
	\item Evaluation metrics. Metrics for evaluation (Accuracy, train error, confusion matrix, ...)
	\item How are the splits (initial pool, initial training data) generated
	\item initial labeled pool sizes
	\item stream based: if 10.000 instances are pooled but none are accepted, training is finished early.
\end{itemize}
